\thetitle

### 2021-03-02 writing/challenges.tex
touching up 4.0

However, three challenges remain:  comparing the effect of
blame on the rational programmer across three different mechanisms; the
collection of a large number of representative debugging scenarios;  and a
proper sampling strategy for the huge space of possibilities. A
coincidental challenge is the disparity of the implementations of
gradually typed languages. To eliminate this variable from the comparison,
this paper uses Racket, which is thus far the only language in which all
three major soundness mechanisms are available in a reasonably robust and
directly comparable manner; for the implementation of the transient
semantics, see the parallel submission of an experience
report~\cite{ttt21}.

The {\em first challenge\/} stems from the differences between the blame
assignment mechanisms of the three semantic variants.  While Natural
assigns blame to {\em one\/} component, Transient assigns blame to a
sequence of components. The Erasure semantics does not blame a component
{\it per se\/}, but it comes with an exception location and a stack trace,
which implicitly suggests parties to blame.  The different strategies
greatly affect the behavior of the rational programmer (and real
programmers, too).

>>>>

Three challenges remain, however: comparing the effect of blame on the rational
programmer across three different mechanisms; the collection of a large number
of representative debugging scenarios; and a proper sampling strategy for the
huge space of possibilities. A coincidental challenge is the disparity of the
implementations of gradually typed languages. To eliminate this variable, this
authors use Racket, which is thus far the only language in which all three major
soundness mechanisms are available in a reasonably robust and comparable manner;
for the implementation of the transient semantics, see the parallel submission
of an experience report~\cite{ttt21}.

The {\em first challenge\/} stems from the differences between the blame
assignment mechanisms of the three semantic variants.  While Natural assigns
blame to {\em one\/} component, Transient assigns blame to a sequence of
components. The Erasure semantics does not blame components {\it per se\/}. But,
it comes with an exception location and a stack trace, which implicitly suggests
parties to blame.  Each strategy affects the behavior of the rational programmer
differently (and real ones, too).
